---
title: "Center for Ocean Forecasting"
output:
  html_document:
    df_print: paged
---
Center for Ocean Forecasting

```{r setup, message = FALSE, echo = FALSE}
knitr::opts_chunk$set(cache=TRUE)
library(dplyr)
library(obpg2tools)
library(stars)
library(ggplot2)
library(sf)
```



## Data Sources

**Observation Sources**

 - Satellites (OBPG, MUR, Copernicus, ...)
 - Buoys
 - Weather stations
 - Interpolated historical weather (DAYMET)
 - River flow
 - Species Observations

**Model Sources**

 - NOAA/NWS weather models
 - RTOFS ocean models
 - NECOFS ocean models


## Example Satellite Data
```{r read_db}
data_path = obpg_path("nwa", "AQUA_MODIS", "L3m")
db = read_database(data_path)
db
```

## Pull SST December 2020
```{r pull_sst}
db_sst = db %>%
  filter(param == "sst" &
         per == "8DR" &
         between(date, as.Date("2020-12-01"), as.Date("2020-12-31")))
db_sst
```

## compose SST filenames
```{r compose_files}
sst_files = compose_obpg(db_sst, data_path)
head(sst_files, n = 6)
```

## read SST files

```{r read_files}
sst = read_stars(sst_files, along = 'band') %>%
  st_set_dimensions(which = 'band', values = db_sst$date)
sst
```

## plot SST rasters

```{r show_one, echo = FALSE, message = FALSE}
ggplot() +
  geom_stars(data = sst[,,,1:3]) +
  coord_equal() +
  facet_wrap(~band) +
  guides(fill=guide_legend(title="SST")) +
  theme_void() +
  scale_x_discrete(expand=c(0,0)) +
  scale_y_discrete(expand=c(0,0))
```
## Drill out a point

```{r point}
point <- dplyr::tibble(id = "1", lon = -68.70557, lat = 43.04157) %>%
  st_as_sf(coords = c("lon", "lat"), crs = st_crs(sst))

p_values = st_extract(sst, point) %>% st_as_sf()
```


