---
title: "Center for Ocean Forecasting"
output:
  html_document:
    df_print: paged
---
Center for Ocean Forecasting

```{r setup, message = FALSE, echo = FALSE}
knitr::opts_chunk$set(cache=TRUE)
library(tidyr)
library(dplyr)
library(obpg2tools)
library(stars)
library(ggplot2)
library(sf)
```



## Data Sources

**Observation Sources**

 - Satellites (OBPG, MUR, Copernicus, ...)
 - Buoys
 - Weather stations
 - Interpolated historical weather (DAYMET)
 - River flow
 - Species Observations

**Model Sources**

 - NOAA/NWS weather models
 - RTOFS ocean models
 - NECOFS ocean models


## Example Satellite Data
```{r read_db}
data_path = obpg_path("nwa", "AQUA_MODIS", "L3m")
db = read_database(data_path)
db
```

## Pull SST December 2020
```{r pull_sst}
db_sst = db %>%
  filter(param == "sst" &
         per == "8DR" &
         between(date, as.Date("2020-12-01"), as.Date("2020-12-31")))
db_sst
```

## compose SST filenames
```{r compose_files}
sst_files = compose_obpg(db_sst, data_path)
head(sst_files, n = 6)
```

## read SST files

```{r read_files}
sst = read_stars(sst_files, along = 'band') %>%
  st_set_dimensions(which = 'band', values = db_sst$date)
sst
```

## plot SST rasters (just first 4 days)

```{r drill_point, echo = FALSE}
point <- dplyr::tibble(id = "1", lon = -68.70557, lat = 43.04157) %>%
  st_as_sf(coords = c("lon", "lat"), crs = st_crs(sst))

p_values = st_extract(sst, point) %>% 
  st_as_sf() %>% 
  st_drop_geometry() %>%
  as_tibble() %>% 
  pivot_longer(everything(), names_to = "date", values_to = "sst") %>%
  mutate(date = as.Date(date))
```

And show a point in Gulf of Maine we'll extract.

```{r show_one, echo = FALSE, message = FALSE}
plot(sst[,,,1:4], 
     hook = function(){plot(point, 
                            add = TRUE, 
                            col = "orange", 
                            cex = 2, 
                            pch = 16)})

```

## Drill out a point in the Gulf of Maine

```{r plot_point, echo = FALSE, message = FALSE, warning = FALSE}
ggplot(data = p_values, aes(date, sst)) + 
  geom_point() + 
  geom_line(col = "blue") + 
  labs(x = "Date", y = "SST", title = "December, 2020") +
  ylim(c(5, 15))
```

What is that break about? And why does the 8-day rolling mean temperature drop like that?

```{r all_plot, echo = FALSE, warning = FALSE}
plot(sst, key.pos = NULL,
     hook = function(){plot(point, 
                            add = TRUE, 
                            col = "orange", 
                            cex = 3, 
                            pch = 1)})
```


